---
title: "{{title}}"
date: "`r Sys.Date()`"
output:
  html_document:
    theme: cosmo
    toc: true
    toc_float: true
    highlight: tango
    fig_width: 8
    fig_height: 6
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = {{include_code}}, warning = FALSE, message = FALSE)
library(DT)
library(ggplot2)
```

## Study Overview

This report presents power analysis results for a virome study with the following parameters:

- Number of viral taxa analyzed: **{{n_viruses}}**
- Expected effect size (fold change): **{{effect_size}}**
- Statistical significance level (α): **{{alpha}}**
- Sparsity (proportion of zeros): **{{sparsity}}**
- Statistical test method: **{{method}}**

## Power Analysis Results

### Statistical Power

With **{{n_samples}}** samples per group, the estimated statistical power is **{{power}}**.

This means there is a **{{power_pct}}%** probability of detecting a true effect of the specified size.

```{r power-plot, echo=FALSE}
# Power curve plot would be embedded here
```

### Sample Size Recommendation

To achieve **{{target_power}}%** power, we recommend a minimum of **{{recommended_sample_size}}** samples per group.

## Distribution of Significant Features

At the recommended sample size, we expect to detect approximately **{{expected_discoveries}}** differentially abundant viral taxa.

```{r features-table, echo=FALSE}
# DT::datatable would be used here to show expected discoveries
```

## Assumptions and Limitations

- This analysis assumes a negative binomial distribution of viral counts
- Multiple testing correction using the Benjamini-Hochberg method
- Power may be lower for extremely rare viral taxa
- Actual power depends on true biological variability

## Interactive Power Calculator

Adjust parameters to explore different scenarios:

```{r interactive, echo=FALSE}
# Shiny widget would be embedded here
```

## References

1. McMurdie PJ, Holmes S (2014). "Waste Not, Want Not: Why Rarefying Microbiome Data Is Inadmissible." PLoS Computational Biology, 10(4), e1003531.
2. Love MI, Huber W, Anders S (2014). "Moderated estimation of fold change and dispersion for RNA-seq data with DESeq2." Genome Biology, 15(12), 550.
3. Xia F, Chen J, Fung WK, Li H (2013). "A logistic normal multinomial regression model for microbiome compositional data analysis." Biometrics, 69(4), 1053-1063.

---

<p style="text-align: center;">Generated with viromePower package</p>